\bf Title here

### 2020-08-26 paper/paper.Rmd
the index function should be a mapping from the projected data space (R^{nxd}) rather than R^{pxd}

Let $\mathbf{X}_{n \times p}$ be the data matrix, an n-d projection can be seen as a linear transformation $T: \mathbb{R}^p \mapsto \mathbb{R}^d$ defined by $\mathbf{P} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{P}_{n \times d}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection basis. Define $f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}$ to be an index function that maps the projection basis $\mathbf{A}$ onto an index value $I$, this function is commonly known as the projection pursuit index (PPI) function, or the index function and is used to measure the "interestingness" of a projection. A number of index functions have been proposed in the literature to detect different data structures, including Legendre index [@friedman1974projection], Hermite index [@hall1989polynomial], natural Hermite index [@cook1993projection], chi-square index [@posse1995projection], LDA index [@lee2005projection] and PDA index [@lee2010projection].

>>>>

Let $\mathbf{X}_{n \times p}$ be the data matrix, an n-d projection can be seen as a linear transformation $T: \mathbb{R}^p \mapsto \mathbb{R}^d$ defined by $\mathbf{P} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{P}_{n \times d}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection basis. Define $f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}$ to be an index function that maps the projection basis $\mathbf{A}$ onto an index value $I$, this function is commonly known as the projection pursuit index (PPI) function, or the index function and is used to measure the "interestingness" of a projection. A number of index functions have been proposed in the literature to detect different data structures, including Legendre index [@friedman1974projection], Hermite index [@hall1989polynomial], natural Hermite index [@cook1993projection], chi-square index [@posse1995projection], LDA index [@lee2005projection] and PDA index [@lee2010projection].

### 2020-08-26 paper/paper.tex
the index function should be a mapping from the projected data space (R^{nxd}) rather than R^{pxd}

Let \(\mathbf{X}_{n \times p}\) be the data matrix, an n-d projection
can be seen as a linear transformation
\(T: \mathbb{R}^p \mapsto \mathbb{R}^d\) defined by
\(\mathbf{P} = \mathbf{X} \cdot \mathbf{A}\), where
\(\mathbf{P}_{n \times d}\) is the projected data and
\(\mathbf{A}_{p\times d}\) is the projection basis. Define
\(f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}\) to be an index
function that maps the projection basis \(\mathbf{A}\) onto an index
value \(I\), this function is commonly known as the projection pursuit
index (PPI) function, or the index function and is used to measure the
``interestingness'' of a projection. A number of index functions have
been proposed in the literature to detect different data structures,
including Legendre index \citep{friedman1974projection}, Hermite index
\citep{hall1989polynomial}, natural Hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}.

>>>>

Let \(\mathbf{X}_{n \times p}\) be the data matrix, an n-d projection
can be seen as a linear transformation
\(T: \mathbb{R}^p \mapsto \mathbb{R}^d\) defined by
\(\mathbf{P} = \mathbf{X} \cdot \mathbf{A}\), where
\(\mathbf{P}_{n \times d}\) is the projected data and
\(\mathbf{A}_{p\times d}\) is the projection basis. Define
\(f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}\) to be an index
function that maps the projection basis \(\mathbf{A}\) onto an index
value \(I\), this function is commonly known as the projection pursuit
index (PPI) function, or the index function and is used to measure the
``interestingness'' of a projection. A number of index functions have
been proposed in the literature to detect different data structures,
including Legendre index \citep{friedman1974projection}, Hermite index
\citep{hall1989polynomial}, natural Hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}.
